Manuscript

### 2023-12-07 notebook/manuscript.qmd
Make the manuscript a target
Correctly render the appendix and manuscript with targets

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
# targets::tar_load(c(manuscript_nice, manuscript_manuscripty))
```

>>>>

```{r include=FALSE}
# Add the manuscript target as a dependency to the overall website
targets::tar_load(
  c(manuscript_nice, manuscript_manuscripty,
    appendix_nice, appendix_manuscripty)
)
```
